### 2020-04-26 final_report/results.tex
more detailed figure 11
update fig. 12 caption

\begin{figure}[h]
	\centering
	\begin{subfigure}[b]{0.333\textwidth}
		\centering
		\includegraphics[width=\linewidth]{scaling_metric_r2}
		% TODO: only a placeholder, regenerate when data becomes available
		\caption{Regression performance (as $R^2$)}
	\end{subfigure}\hfill%
	\begin{subfigure}[b]{0.333\textwidth}
		\centering
		\includegraphics[width=\linewidth]{scaling_time_train}
		% TODO: only a placeholder, regenerate when data becomes available
		\caption{Mean training time}
	\end{subfigure}\hfill%
	\begin{subfigure}[b]{0.333\textwidth}
		\centering
		\includegraphics[width=\linewidth]{scaling_time_pred}
		% TODO: only a placeholder, regenerate when data becomes available
		\caption{Mean prediction time}
	\end{subfigure}
	\caption{Various metrics collected during experiment 3 (scaling
	benchmark) displayed as a function of training set size.}
	\label{fig:scaling}
\end{figure}

@@

	\begin{subfigure}[b]{0.25\textwidth}
		\centering
		\includegraphics[width=\linewidth]{run1_5ke_1h3f128_4974_performance}
		% TODO: only a placeholder, regenerate when data becomes available
	\end{subfigure}\hfill%
	\begin{subfigure}[b]{0.25\textwidth}
		\centering
		\includegraphics[width=\linewidth]{run1_5ke_1h3f128_4974_performance}
		% TODO: only a placeholder, regenerate when data becomes available
	\end{subfigure}\hfill%
	\begin{subfigure}[b]{0.25\textwidth}
		\centering
		\includegraphics[width=\linewidth]{run1_5ke_1h3f128_4974_performance}
		% TODO: only a placeholder, regenerate when data becomes available
	\end{subfigure}\hfill%
	\begin{subfigure}[b]{0.25\textwidth}
		\centering
		\includegraphics[width=\linewidth]{run1_5ke_1h3f128_4974_performance}
		% TODO: only a placeholder, regenerate when data becomes available
	\end{subfigure}
	\caption{Regression performance of selected best-performing models trained in experiment~4.}
	\label{fig:reg-performance}
\end{figure}

>>>>

\begin{figure}[h]
	\centering
	\begin{subfigure}[b]{0.333\textwidth}
		\centering
		\includegraphics[width=\linewidth]{scaling_metric_r2}
		% TODO: only a placeholder, regenerate when data becomes available
		\caption{Regression performance (as $R^2$)}
	\end{subfigure}\hfill%
	\begin{subfigure}[b]{0.333\textwidth}
		\centering
		\includegraphics[width=\linewidth]{scaling_time_train}
		% TODO: only a placeholder, regenerate when data becomes available
		\caption{Complexity (as~$\overline{t}_{\text{trn.}}$)}
	\end{subfigure}\hfill%
	\begin{subfigure}[b]{0.333\textwidth}
		\centering
		\includegraphics[width=\linewidth]{scaling_time_pred}
		% TODO: only a placeholder, regenerate when data becomes available
		\caption{Complexity (as~$\overline{t}_{\text{pred.}}$)}
	\end{subfigure}
	\caption{Various metrics collected during experiment 3 (scaling
	benchmark) displayed as a function of training set size.}
	\label{fig:scaling}
\end{figure}

@@

	\begin{subfigure}[b]{0.25\textwidth}
		\centering
		\includegraphics[width=\linewidth]{run1_5ke_1h3f128_4974_performance}
		% TODO: only a placeholder, regenerate when data becomes available
	\end{subfigure}\hfill%
	\begin{subfigure}[b]{0.25\textwidth}
		\centering
		\includegraphics[width=\linewidth]{run1_5ke_1h3f128_4974_performance}
		% TODO: only a placeholder, regenerate when data becomes available
	\end{subfigure}\hfill%
	\begin{subfigure}[b]{0.25\textwidth}
		\centering
		\includegraphics[width=\linewidth]{run1_5ke_1h3f128_4974_performance}
		% TODO: only a placeholder, regenerate when data becomes available
	\end{subfigure}\hfill%
	\begin{subfigure}[b]{0.25\textwidth}
		\centering
		\includegraphics[width=\linewidth]{run1_5ke_1h3f128_4974_performance}
		% TODO: only a placeholder, regenerate when data becomes available
	\end{subfigure}
	\caption{Regression performance of models 1-4 (row 1, from the left) and 5-8
		(row 2) trained in experiment~4 (competitive surrogate training), viewed
		as true vs. predicted TBR on a test set of a selected cross-validation
		fold. Due to large set sizes, points are randomly subsampled and coloured by density.}
	\label{fig:reg-performance}
\end{figure}
